Manuscript Figures

### 2021-09-16 src/manuscript_figures.Rmd
fix panel titles for survival figures

# survival plots
gbm_surv <- read.csv(file.path(folder, "survival_time_response_and_predictions.csv"), row.names = 1)
gbm_surv <- gbm_surv[,c(3, 5:7)]
panel_titles <- c('observed response', 'MAUI + MGMT', 
                  'MAUI + MGMT-expression', 'MAUI + MGMT-methylation')
plots <- sapply(simplify = F, 1:ncol(gbm_surv), function(i) {
  x <- colnames(gbm_surv)[i]
  plot_survival(surv, partition.df = gbm_surv[,x,drop = F], duration_col = 'PFI.time', event_col = 'PFI')[['plot']] + 
    ggtitle(label = panel_titles[i]) + theme(legend.direction = 'vertical', legend.title = element_blank(), 
                                             legend.position = c(0.5, 0.8))
})

>>>>

# survival plots
gbm_surv <- read.csv(file.path(folder, "survival_time_response_and_predictions.csv"), row.names = 1)
gbm_surv <- gbm_surv[,c(3, 5:7)]
panel_titles <- c('observed response', 'MAUI + MGMT', 
                  'MGMT-expression', 'MGMT-methylation')
plots <- sapply(simplify = F, 1:ncol(gbm_surv), function(i) {
  x <- colnames(gbm_surv)[i]
  plot_survival(surv, partition.df = gbm_surv[,x,drop = F], duration_col = 'PFI.time', event_col = 'PFI')[['plot']] + 
    ggtitle(label = panel_titles[i]) + theme(legend.direction = 'vertical', legend.title = element_blank(), 
                                             legend.position = c(0.5, 0.8))
})
